---
title: "Job Application Text Mining Widget"
output: html_notebook
---


The purpose of this widget is to analyze any job application and extract the most common keywords to help optimize resume to score well on automated resume filtering algorithms.

Note to self: Do a bit of reading on which algorithms are used for ranking and how they work


```{r}
library(tidytext)
library(dplyr)
library(tidyr)
library(tidyselect)
library(broom)
library(rlang)
```



First we read in the single text document. Each document is first broken down into a new row for each non-breaking space as indicated by " \xa0 " . Note: stringsAsFactors must be FALSE in order for the data format to work with tibble

```{r}
setwd("D:/R Demo WD/")
text <- read.table(file="DS_intern_text.txt", header = FALSE, sep = "\xa0", stringsAsFactors = FALSE)
```


We can see the text as a list here
```{r}
View(text)
```

Now we will transform it to the tidytext format by using tibble to shape it into a dataframe
```{r}
dftext <- tibble(line = 1:dim(text)[1], text = text$V1)

View(dftext)


str(dftext)
```


Next we will tokenize the remaining lists, until we reach tidytext format as shown below
```{r}
dftext <- dftext %>%
  unnest_tokens(word, text)
```


Finally we can remove stopwords to clean up the corpus

Note: Try do do this as an SQL exercise!
```{r}
data("stop_words")

tidy_text <- dftext %>% 
  anti_join(stop_words)

View(tidy_text)
```


Now we can do some descriptive analysis

```{r}
library(ggplot2)

tidy_text %>%
  count(word, sort = TRUE) %>%
  filter(n > 1) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```
































Shortcuts Reminder


Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
